\documentclass[../setup.tex]{subfiles}

\begin{document}
\subsection{Using Prebuilt Resources}
Set up on the CSC machines is a lot simpler because all of the resources are managed for you.
Therefore, all you need to do is to add the provided definitions to your \lstinline{~/.bashrc}.
\begin{lstlisting}
  # C415 Predefinitions
  source "/cshome/c415/415-resources/415env.sh"
\end{lstlisting}
This should enable you to build manually using the command line.

\subsection{Installing CLion}
\begin{enumerate}
  \item
    Go to the \href{https://www.jetbrains.com/clion/download/\#section=linux} {download page} and
    download \textit{CLion} for Linux.
  \item
    Assuming you've downloaded the tarball to your \lstinline{~/Downloads} folder, you can extract
    it to your home directory using the following command:
    \begin{lstlisting}
      sudo tar -xzf ~/Downloads/CLion-<version>.tar.gz -C ~
    \end{lstlisting}
    If you are confident about your ability to setup your own install you can put it
    elsewhere but you will be on your own.
  \item
    From now on, you can start \textit{CLion} by using the following command:
    \begin{lstlisting}
      ~/CLion-<version>/bin/clion.sh
    \end{lstlisting}
  \item
    Perform the initial set up of CLion.
    \begin{enumerate}
      \item
        Select \texttt{Do not import settings} and click \texttt{OK}.
      \item
        Scroll to the bottom of the license agreement then hit \texttt{Accept}.
      \item
        Choose if you want to share usage statistics.
      \item
        You should be presented with a prompt for your license. Select \texttt{Activate},
        \texttt{JetBrains Account}, enter your UAlberta email address and JetBrains password.
        Click the \texttt{Activate} button.
      \item
        Pick your favorite UI. Then click \texttt{Next: Toolchains}.
      \item
        Click \texttt{Next: Default Plugins}.
      \item
        You might consider disabling all but the git plugin, and even then, using it is up to you.
        It can be useful to see the color coded files for differences at a glance or track changes
        in a file. You should consider disabling all of the web development plugins. Disabling
        other tools is up to you as well. Now select \texttt{Next: Feature Plugins}
      \item
        Again, the choices here are yours. If you like vim, then maybe the vim plugin is up your
        alley. The markdown plugin can be useful as well. You do not need the TeamCity Integration,
        the Lua integration, nor the Swift integration. Select \texttt{Start using CLion}
    \end{enumerate}
\end{enumerate}

\end{document}
